Data Specialization for a Staged Lambda Calculus

### 2015-02-22 paper/abstract.tex
various fixes
tweak abstract to line up with intro

In this paper, we provide a theoretical understanding of this splitting process
by defining it as a program transformation on \lang, a typed lambda calculus
equipped with a modal staging operator. This approach extends splitting to
language features absent in prior work, including first-order functions and
disjoint unions.

@@

\TODO (Is this true?)
We also show that splitting a staged implementation of an interpreter yields a
partial evaluator.

%into one function per stage, performing all the work depending only on the
%available inputs.

%as much work as possible given the inputs available at each stage.

%In this way, splitting is essentially an algorithm generation technique.

% amortized

>>>>

Prior work on splitting has been limited to simple, imperative languages; in
this paper, we extend splitting to \lang, a typed lambda calculus equipped with
a modal staging operator, allowing us to split recursive and higher-order
functions.

@@

% something about compositional, cross-cutting code
